Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
@ Grégoire: specify T in subsection VII. A

Experiments are carried out using temporal-scattering coefficients as well as Mel Frequency Cesptral Coefficients (MFCCs) as features. For the temporal-scattering, each scene is described by 128 vectors of scattering coefficients \gl{vincent: windows and hops ?}. Experiments are conducted with and without the logarithmic compression (see Section \ref{sec:logcomp}).

>>>>

Experiments are carried out using temporal-scattering coefficients as well as Mel Frequency Cesptral Coefficients (MFCCs) as features. For the temporal-scattering, each scene is described by 128 vectors of scattering coefficients, with half-overlapping windows $\boldsymbol{\phi}(t)$ of duration $T=188\,\mathrm{ms}$. Experiments are conducted with and without the logarithmic compression (see Section \ref{sec:logcomp}).
